---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# swtp

[![CircleCI](https://circleci.com/gh/bocinsky/swtp.svg?style=shield&circle-token=182c3ee96956e3cc5eac1044a4c177ac28d39d91)](https://circleci.com/gh/bocinsky/swtp)

This repository contains the data and code for our paper:

> Bocinsky, R. Kyle, Tiffany Clark, and Katherine A. Spielmann, (2019). _The Southwestern Taphonomic Protocol_. **In review.**

### How to cite

Please cite this compendium as:

> Bocinsky, R. Kyle, Tiffany Clark, and Katherine A. Spielmann, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for 'The Southwestern Taphonomic Protocol'_. Accessed `r format(Sys.Date(), "%d %b %Y")`.

### How to download or install

You can install this compendium as an R package, swtp, from GitHub with:
```{r gh-installation, eval = FALSE}
# install.packages("remotes")
remotes::install_github("bocinsky/swtp")
```

### Building the report
```{r build, eval = FALSE}
rmarkdown::render("./paper/swtp.Rmd", 
                  output_file = "index.html", 
                  output_dir = "./docs")
```

### Licenses

**Text and figures:**  [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)

**Code:** See the [DESCRIPTION](DESCRIPTION) file

**Data:** [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse
