---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# swtp

[![CircleCI](https://circleci.com/gh/bocinsky/swtp.svg?style=shield&circle-token=182c3ee96956e3cc5eac1044a4c177ac28d39d91)](https://circleci.com/gh/bocinsky/swtp)

This repository contains the data and code for our paper:

> Bocinsky, R. Kyle, Tiffany Clark, and Katherine A. Spielmann, *In review*. _The Southwestern Taphonomic Protocol_. **In review.**

### How to cite

Please cite this compendium as:

> Bocinsky, R. Kyle, Tiffany Clark, and Katherine A. Spielmann, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for 'The Southwestern Taphonomic Protocol'_. Accessed `r format(Sys.Date(), "%d %b %Y")`.

## Contents

The [:file_folder: paper](/paper) directory contains:  

- [:page_facing_up: paper](/paper/swtp.Rmd): R Markdown source document for the manuscript. Includes code to reproduce the figures and tables generated by the analysis. It also has a rendered version, `robinson2020.pdf`, suitable for reading (the code is replaced by figures and tables in this file).
- [:file_folder: data](/paper/data): Data used in the analysis.  
- [:file_folder: tables](/analysis/tables): Tables presented in the analysis.
- [:file_folder: screenshots](/analysis/screenshots): Screenshots presented in the analysis.

## How to run in your browser or download and run locally

You can download the compendium as a zip from from this URL: [master.zip](/archive/master.zip). After unzipping, open the `Proj` file in RStudio, and run `devtools::install()` to ensure you have the packages this analysis depends on (also listed in the [DESCRIPTION](/DESCRIPTION) file). Then open `robinson2020.Rmd` and knit to produce the paper in PDF format.

Or, simply install straight from Github:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("bocinsky/swtp")
```

### Licenses

**Text and figures :**  [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)

**Code :** [GNU GPLv3](LICENSE.md)

**Data :** [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse

### Contributions

We welcome contributions from everyone. Before you get started, please see our [contributor guidelines](CONTRIBUTING.md). Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.

### Acknowledgements

This compendium was created using the [`rrtools` package by Ben Marwick](https://github.com/benmarwick/rrtools), which is ✨ pure magic ✨ for doing reproducible research. 
